### 2023-06-21 ms.qmd
Updates Methods

The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*Lampropholis guichenoti*) and the rainbow skink or delicate skink (*L. delicata*). These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple2011]). They also have similar breeding periods, but with some differences in reproductive output: while *L. delicata* lays 1 to 6 eggs in only one clutch per season, *L. guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple2011]; 2014). This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.

@@

To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig. 2) (see Leal and Powell, 2012; Clark *et al.*, 2013). First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below). We divided this training phase into three stages (see Fig. 2): in the first stage, lizards had to eat a small, frozen cricket (*A. domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure; in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps; and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage. Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away. At the end of the experiment, we recorded whether the cricket has been consumed or not. Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials. This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase (see Supplementary material).

>>>>

The subjects in our experiments were juveniles from two species of skinks, the common garden skink (*Lampropholis guichenoti*) and the rainbow skink or delicate skink (*L. delicata*). These are small (∼35--55 mm snout-vent length (SVL)), oviparous, and generalist skinks that usually share the same habitat in suburban areas throughout south-eastern Australia ([@chapple_know_2011]). They also have similar breeding periods, but with some differences in reproductive output: while *L. delicata* lays 1 to 6 eggs in only one clutch per season, *L. guichenoti* clutches are smaller (1-5 eggs per clutch) but they usually lay two clutches per season ([@chapple_know_2011]; [@chapple_biology_2014]). This difference in reproductive output through the breeding season may involve different degree of sensitivity to maternal effects and its interaction with other aspects of early environment.

@@

To estimate learning skills, we tested skinks' ability to locate a food reward in a series of behavioural tasks (Fig. 2) (see [@leal_behavioural_2012]; [@clark_colour_2014]). First, we performed a training phase where lizards had to learn to eat from white 3D-printed PLA ramps (9 L x 4 W x 5 H cm) identical to the ones from the experiment except for the colour (see below). We divided this training phase into three stages (see Fig. 2): in the first stage, lizards had to eat a small, frozen cricket (*A. domestica*) from an opaque petri dish (3D x 1.6H cm) placed in the middle of their enclosure; in the second stage, the petri dish with the cricket was placed on top of the white 3D printed ramps; and finally, the cricket was left inside a well (3D x 1.75H cm) on the top of the ramp in the third and last stage. Every trial began when we left the feeding block (petri dish, ramp, or both) inside the enclosure and finished one hour later when we took it away. At the end of the experiment, we recorded whether the cricket has been consumed or not. Trial was considered successful if the lizard could locate and consume the reward, while completion of each stage required the lizards to eat the crickets in at least 5 out of 6 trials. This phase lasted 38 days until all the lizards were able to eat from the ramp; only in one case we decided not to use the lizard because its behaviour was not consistent over the course of the training phase (see Supplementary material).
